Index measures for oak decline severity using phenotypic descriptors

### 2019-12-14 manuscript/manuscript.Rmd
DAI response surface method added

A similar process was used for the DAI using also a comparison between active bleed size and black staining size as well as missing crown and crown transparency.
Cases included neutral, moderate and severe AOD and COD decline types.

- reduced by a factor of 16 for clearer visualisation

>>>>

```{r stem_symptom_ranges}
symptom_ranges <- site_corrected_analysis_suitable_data %>%
  select(`Active bleed size (mm)`,`Black staining size (mm)`) %>%
  gather(descriptor,value) %>%
  group_by(descriptor) %>%
  summarise(minimum = min(value),
             maximum = max(value),
             center = minimum + (maximum - minimum) / 2
             )
```

The same approach was used for the DAI using also a comparison between active bleed size and black staining size () as well as missing crown and crown transparency.
The upper boundary for the ranges of active bleed size and black stain size was taken as the center value between the maximum and minimum and reduced by a factor of eight to give ranges of `r glue("{symptom_ranges$minimum[1]}-{signif(symptom_ranges$center[1] / 8,digits = 3)}mm")` and `r glue("{symptom_ranges$minimum[2]}-{signif(symptom_ranges$center[2] / 8,digits = 3)}mm")` respectively and enable more effective visualisation.
Cases included neutral, moderate and severe with DAI scores closest to 0, 0.5 and 1 respectively for AOD and 0, -0.5 and -1 respectively for COD.
